---
title: ""
header-includes:
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
  - \usepackage{graphicx}
  - \setlength{\parskip}{1em}
  - \usepackage{leading}
  - \leading{5pt}
output:
  pdf_document: 
    extra_dependencies: ["float","booktabs" ]
params:
  diffResultsTable: NA
  diffParamsTables: NA
  diffTrajectoryGGPlot: NA
  diffPositivityGGPlot: NA
  autoTextStrings: NA
---

```{r intro, include=FALSE}

options(knitr.table.format = "latex")

defaultW <- getOption("warn") 
options(warn = -1)


```

## CovidU: Comparison Report ^[This report was generated using the CovidU app, from Harvard IQSS. For more information, see iq.harvard.edu/covidu] 

`r "**Scenarios Evaluated:**  \n"`
`r paste0("|            ", params$autoTextStrings$treatmentString) `
`r paste0("|            ", params$autoTextStrings$controlString) `

Parameters not listed on this page are held constant at values listed on pages 2 and 3.

`r params$autoTextStrings$takeAwayString `

`r   if(nrow(params$diffParamsTables$diffBasicTable) > 0) {"**Changes in Basic Parameters**"} else {""}`
```{r basicTable, echo = FALSE,comment=NA,background=NA}
if(nrow(params$diffParamsTables$diffBasicTable) > 0){  
  params$diffParamsTables$diffBasicTable %>% kable(align = "lcr", row.names = FALSE, col.names = NULL, booktabs = TRUE, format = "latex") %>%
    kable_styling(latex_options = c("striped"), font_size = 8, position = "center")
}
```
`r   if(nrow(params$diffParamsTables$diffTestTable) > 0) {"**Changes in Testing Assumptions**"} else {""}`
```{r testTable, echo = FALSE,comment=NA,background=NA}
if(nrow(params$diffParamsTables$diffTestTable) > 0){  
  params$diffParamsTables$diffTestTable%>% kable(align = "lcr", row.names = FALSE, col.names = NULL, booktabs = TRUE, format = "latex") %>%
    kable_styling(latex_options = c("striped"), font_size = 8, position = "center")
}

```
`r   if(nrow(params$diffParamsTables$diffPopsocTable) > 0) {"**Changes in Population and Social Assumptions**"} else {""}`
```{r popsocTable, echo = FALSE,comment=NA,background=NA}
if(nrow(params$diffParamsTables$diffPopsocTable) > 0){  
  params$diffParamsTables$diffPopsocTable%>% kable(align = "lcr", row.names = FALSE, col.names = NULL, booktabs = TRUE, format = "latex") %>%
    kable_styling(latex_options = c("striped"), font_size = 8, position = "center")
}

```
`r   if(nrow(params$diffParamsTables$diffExtraTable) > 0) {"**Changes in Additional Assumptions**"} else {""}`
```{r extraTable, echo = FALSE,comment=NA,background=NA}
if(nrow(params$diffParamsTables$diffExtraTable) > 0){  
  params$diffParamsTables$diffExtraTable%>% kable(align = "lcr", row.names = FALSE, col.names = NULL, booktabs = TRUE, format = "latex") %>%
    kable_styling(latex_options = c("striped"), font_size = 8, position = "center")
}

```

**Changes in Results**
```{r resultsTable, echo = FALSE,comment=NA,background=NA}
  
params$diffResultsTable %>% kable(align = "lc", row.names = FALSE, col.names = NULL, booktabs = TRUE, format = "latex") %>%
    kable_styling(latex_options = c("striped"), font_size = 8, position = "center")


```
    

```{r charts, echo = FALSE, fig.height=3.75}
grid.arrange(params$diffTrajectoryGGPlot, params$diffPositivityGGPlot, ncol = 2)
```



```{r end, include = FALSE}

options(warn = defaultW)

```